\textls[-0]{\thetitle}

### 2023-03-18 canonicitymodel.tex
Fix canonicity model, reply comments.

  \Glued{\mathit{L}}("nil") &= ( \TyLkg{\LSigEmp} , \denotesC{\top} ) \\
  \Glued{\mathit{L}}((A,s,T) :: tl) &= {\Glued{\mathit{L}}(tl)}(\gm) \times^\bullet \GluedPi{A}{T} \quad \text{($\times^\bullet$ is a special case for $\Glued{\Sigma}$)}  \\

@@

  \denotesC{\goodType{\Gm}{\TyLkg{\lsig}}{}} &= \Gmodel{\Glued{\mathit{L}}(\denotesC{\lsig})} \quad \text{ discard syntax info} \\
  \denotesC{\goodType{\Gm}{\TyTkg{\lsig}}{}} &= \Gmodel{\Glued{\mathit{P}}(\denotesC{\lsig})} \\

@@

  \denotesC{\goodTerm{\Gm}{\LkgAdd{\lkg}{t}}{\TyLkg{\LSigAdd{\lsig}{s}{T}}}} &= \Gmodel{\Gpair{\denotesCC{\lkg}}{\Glam{\denotesCC{t}}}} \\

@@

  \denotesC{\goodTerm{\Gm}{\lkgproj{1}{\lkg}}{\TyTkg{\lsig}}} &= \Gmodel{\Gfst{\denotesCC{\lkg}}} \\
  \denotesC{\goodTerm{\Gm, \lsigprojT{\lsig}}{\lkgproj{2}{\lkg}}{T}} &= \Gmodel{\Gapp{\Gsnd{\denotesCC{\lkg}}}} \\

>>>>

  \mathit{L}("nil") &=  \denotesC{\top}  \\
  \mathit{L}((A,s,T) :: tl)(\gm)(\gm')(t) &= {\mathit{L}(tl)}(\gm)(\gm')(\lkgproj{1}{t}) \times \Gmodel{\GluedPi{A}{T}}(\gm)(\gm')(\lam{\lkgproj{2}{t}})   \\

@@

  \denotesC{\goodType{\Gm}{\TyLkg{\lsig}}{}} &= {\mathit{L}(\denotesC{\lsig})} \\
  \denotesC{\goodType{\Gm}{\TyTkg{\lsig}}{}} &= \Gmodel{\Glued{\mathit{P}}(\denotesC{\lsig})} \quad \text{ discard syntax info}  \\

@@

  \denotesC{\goodTerm{\Gm}{\LkgAdd{\lkg}{t}}{\TyLkg{\LSigAdd{\lsig}{s}{T}}}}(\gm)(\gm') &= (\denotesC{\lkg}(\gm)(\gm') , \Gmodel{\Glam{\denotesCC{t}}}(\gm)(\gm')) \\

@@

  \denotesC{\goodTerm{\Gm}{\lkgproj{1}{\lkg}}{\TyLkg{\lsig}}}(\gm)(\gm') &= \denotesC{\ell}(\gm)(\gm')[0] \quad \text{ take the first element in the tuple} \\
  \denotesC{\goodTerm{\Gm, \lsigprojT{\lsig}}{\lkgproj{2}{\lkg}}{T}}(\gm_+)(\gm_+') &= ((\denotesC{\ell}(\pi_1{\gm_+})(\gm_+'[0]))[1])(\pi_2{\gm_+})(\gm_+'[1]) \\
